Dissertation

### 2023-10-30 Manuscript/igas_e1.tex
adjust igas toy model figure

@@

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={DarkSlateBlue},
  filecolor={Maroon},
  citecolor={DarkSlateBlue},
  urlcolor={DarkSlateBlue},
  pdfcreator={LaTeX via pandoc}}

@@

@@

\subsubsection{Appendix - Project 2 - Experiment
1}\label{appendix---project-2---experiment-1}

\subsection{E1 Appendix}\label{e1-appendix}

\subsubsection{Posterior Predictive
Distributions}\label{posterior-predictive-distributions}

\subsubsection{Empirical vs.~Predicted}\label{empirical-vs.-predicted}

\subsubsection{Different Aggregations}\label{different-aggregations}

>>>>

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={DarkSlateBlue},
  filecolor={Maroon},
  citecolor={DarkSlateBlue},
  urlcolor={DarkSlateBlue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{pacman}\SpecialCharTok{::}\FunctionTok{p\_load}\NormalTok{(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork)}
\FunctionTok{source}\NormalTok{(}\StringTok{\textquotesingle{}../Functions/IGAS\_ProcessFunctions.R\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\[e^{(c\cdot|x-800|)}\]

\[e^{(c\cdot|x-400|)}\]

\[e^{(c\cdot|x-800|)}\] + \[e^{(c\cdot|x-400|)}\]

\[e^{(c_{varied}\cdot|x-800|)}\]

\(e^{(c_{varied}\cdot|x-800|)}\) \(+e^{(c_{varied}\cdot|x-400|)}\)
\(e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}\)

\(e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}\),

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# }

\NormalTok{p}\OtherTok{=}\DecValTok{2}
\NormalTok{c}\OtherTok{\textless{}{-}}\NormalTok{ .}\DecValTok{000002}

\NormalTok{trainingTestingDifference}\OtherTok{=}\DecValTok{2000}\NormalTok{;}
\NormalTok{cvaried}\OtherTok{=}\NormalTok{.}\DecValTok{00002}
\NormalTok{cconstant}\OtherTok{=}\NormalTok{.}\DecValTok{0005}
\NormalTok{simdat }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{x=}\FunctionTok{rep}\NormalTok{(}\FunctionTok{seq}\NormalTok{(}\DecValTok{200}\NormalTok{,}\DecValTok{1000}\NormalTok{),}\DecValTok{3}\NormalTok{),}\AttributeTok{condit=}\FunctionTok{c}\NormalTok{(}\FunctionTok{rep}\NormalTok{(}\StringTok{"varied"}\NormalTok{,}\DecValTok{1602}\NormalTok{),}\FunctionTok{rep}\NormalTok{(}\StringTok{"constant"}\NormalTok{,}\DecValTok{801}\NormalTok{)),}
                     \AttributeTok{train.position=}\FunctionTok{c}\NormalTok{(}\FunctionTok{rep}\NormalTok{(}\DecValTok{400}\NormalTok{,}\DecValTok{801}\NormalTok{),}\FunctionTok{rep}\NormalTok{(}\DecValTok{800}\NormalTok{,}\DecValTok{801}\NormalTok{),}\FunctionTok{rep}\NormalTok{(}\DecValTok{600}\NormalTok{,}\DecValTok{801}\NormalTok{)),}\AttributeTok{c=}\NormalTok{.}\DecValTok{0002}\NormalTok{,}\AttributeTok{p=}\DecValTok{2}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
                     \FunctionTok{mutate}\NormalTok{(}\AttributeTok{c2=}\FunctionTok{ifelse}\NormalTok{(condit}\SpecialCharTok{==}\StringTok{"varied"}\NormalTok{,cvaried,cconstant),}
                            \AttributeTok{genGauss=}\FunctionTok{exp}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{c}\SpecialCharTok{*}\NormalTok{(}\FunctionTok{abs}\NormalTok{((x}\SpecialCharTok{{-}}\NormalTok{train.position)}\SpecialCharTok{\^{}}\NormalTok{p))),}
                            \AttributeTok{genGaussDist=}\FunctionTok{exp}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{c}\SpecialCharTok{*}\NormalTok{(trainingTestingDifference}\SpecialCharTok{+}\FunctionTok{abs}\NormalTok{((x}\SpecialCharTok{{-}}\NormalTok{train.position)}\SpecialCharTok{\^{}}\NormalTok{p))),}
                            \AttributeTok{genGauss2=}\FunctionTok{exp}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{c2}\SpecialCharTok{*}\NormalTok{(}\FunctionTok{abs}\NormalTok{((x}\SpecialCharTok{{-}}\NormalTok{train.position)}\SpecialCharTok{\^{}}\NormalTok{p))),}
                            \AttributeTok{genGaussDist2=}\FunctionTok{exp}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{c2}\SpecialCharTok{*}\NormalTok{(trainingTestingDifference}\SpecialCharTok{+}\FunctionTok{abs}\NormalTok{((x}\SpecialCharTok{{-}}\NormalTok{train.position)}\SpecialCharTok{\^{}}\NormalTok{p))),}
\NormalTok{                            ) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{group\_by}\NormalTok{(x,condit) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{genGauss=}\FunctionTok{mean}\NormalTok{(genGauss),}\AttributeTok{genGauss2=}\FunctionTok{mean}\NormalTok{(genGauss2),}\AttributeTok{genGaussDist=}\FunctionTok{mean}\NormalTok{(genGaussDist),}\AttributeTok{genGaussDist2=}\FunctionTok{mean}\NormalTok{(genGaussDist2),}\AttributeTok{.groups=}\StringTok{\textquotesingle{}keep\textquotesingle{}}\NormalTok{)}

\CommentTok{\#plot(x,exp(c*(trainingTestingDifference+abs(x{-}800)))+exp(c*(trainingTestingDifference+abs(x{-}400)))}

\NormalTok{colorVec}\OtherTok{=}\FunctionTok{c}\NormalTok{(}\StringTok{"darkblue"}\NormalTok{,}\StringTok{"darkred"}\NormalTok{)}
\NormalTok{plotSpecs }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(}\FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{alpha=}\NormalTok{.}\DecValTok{7}\NormalTok{),}\FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values=}\NormalTok{colorVec),}
                  \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{alpha=}\NormalTok{.}\DecValTok{55}\NormalTok{,}\AttributeTok{xintercept =} \FunctionTok{c}\NormalTok{(}\DecValTok{400}\NormalTok{,}\DecValTok{800}\NormalTok{),}\AttributeTok{color=}\NormalTok{colorVec[}\DecValTok{2}\NormalTok{]),}
                  \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{alpha=}\NormalTok{.}\DecValTok{55}\NormalTok{,}\AttributeTok{xintercept =} \FunctionTok{c}\NormalTok{(}\DecValTok{600}\NormalTok{),}\AttributeTok{color=}\NormalTok{colorVec[}\DecValTok{1}\NormalTok{]),}
                  \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{1.05}\NormalTok{)),}
                  \CommentTok{\#xlim(c(250,950)),}
                  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks=}\FunctionTok{seq}\NormalTok{(}\DecValTok{200}\NormalTok{,}\DecValTok{1000}\NormalTok{,}\AttributeTok{by=}\DecValTok{200}\NormalTok{)),}
                  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Test Stimulus"}\NormalTok{),}
                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{455}\NormalTok{,}\AttributeTok{y=}\FloatTok{1.05}\NormalTok{,}\AttributeTok{label=}\StringTok{"Varied"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{455}\NormalTok{,}\AttributeTok{y=}\NormalTok{.}\DecValTok{97}\NormalTok{,}\AttributeTok{label=}\StringTok{"Training"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{662}\NormalTok{,}\AttributeTok{y=}\FloatTok{1.05}\NormalTok{,}\AttributeTok{label=}\StringTok{"Constant"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{657}\NormalTok{,}\AttributeTok{y=}\NormalTok{.}\DecValTok{97}\NormalTok{,}\AttributeTok{label=}\StringTok{"Training"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{855}\NormalTok{,}\AttributeTok{y=}\FloatTok{1.05}\NormalTok{,}\AttributeTok{label=}\StringTok{"Varied"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{855}\NormalTok{,}\AttributeTok{y=}\NormalTok{.}\DecValTok{97}\NormalTok{,}\AttributeTok{label=}\StringTok{"Training"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
                  \FunctionTok{theme}\NormalTok{(}\AttributeTok{panel.border =} \FunctionTok{element\_rect}\NormalTok{(}\AttributeTok{colour =} \StringTok{"black"}\NormalTok{, }\AttributeTok{fill=}\ConstantTok{NA}\NormalTok{, }\AttributeTok{size=}\DecValTok{1}\NormalTok{),}
                        \AttributeTok{legend.position=}\StringTok{"none"}\NormalTok{))}

\NormalTok{ip1 }\OtherTok{\textless{}{-}}\NormalTok{ simdat  }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(x,}\AttributeTok{y=}\NormalTok{genGauss,}\AttributeTok{group=}\NormalTok{condit,}\AttributeTok{col=}\NormalTok{condit))}\SpecialCharTok{+}\NormalTok{plotSpecs}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"Amount of Generalization"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Identical context, 1c"}\NormalTok{)}
\NormalTok{ip2 }\OtherTok{\textless{}{-}}\NormalTok{ simdat }\SpecialCharTok{\%\textgreater{}\%}  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(x,}\AttributeTok{y=}\NormalTok{genGauss2,}\AttributeTok{group=}\NormalTok{condit,}\AttributeTok{col=}\NormalTok{condit))}\SpecialCharTok{+}\NormalTok{plotSpecs}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Identical context, 2c"}\NormalTok{)}
\NormalTok{ip3 }\OtherTok{\textless{}{-}}\NormalTok{ simdat  }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(x,}\AttributeTok{y=}\NormalTok{genGaussDist,}\AttributeTok{group=}\NormalTok{condit,}\AttributeTok{col=}\NormalTok{condit))}\SpecialCharTok{+}\NormalTok{plotSpecs}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"Amount of Generalization"}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Added distance due to context, 1c"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\NormalTok{ip4 }\OtherTok{\textless{}{-}}\NormalTok{ simdat }\SpecialCharTok{\%\textgreater{}\%}  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(x,}\AttributeTok{y=}\NormalTok{genGaussDist2,}\AttributeTok{group=}\NormalTok{condit,}\AttributeTok{col=}\NormalTok{condit))}\SpecialCharTok{+}\NormalTok{plotSpecs}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Added distance due to context, 2c"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\CommentTok{\# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)}

\NormalTok{gtitle}\OtherTok{=}\StringTok{"Figure 9."}
\NormalTok{title }\OtherTok{=} \FunctionTok{ggdraw}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{draw\_label}\NormalTok{(gtitle,}\AttributeTok{fontface =} \StringTok{\textquotesingle{}bold\textquotesingle{}}\NormalTok{,}\AttributeTok{x=}\DecValTok{0}\NormalTok{,}\AttributeTok{hjust=}\DecValTok{0}\NormalTok{,}\AttributeTok{size=}\DecValTok{11}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\FunctionTok{plot\_grid}\NormalTok{(title,}\ConstantTok{NULL}\NormalTok{,ip1,ip2,ip3,ip4,}\AttributeTok{ncol=}\DecValTok{2}\NormalTok{,}\AttributeTok{rel\_heights=}\FunctionTok{c}\NormalTok{(.}\DecValTok{1}\NormalTok{,.}\DecValTok{8}\NormalTok{,.}\DecValTok{8}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

\centering{

\includegraphics{igas_e1_files/figure-pdf/fig-Toy-Model2-1.pdf}

}

\caption{\label{fig-Toy-Model2}A simple model depicting the necessity of
both of two separately fit generalization parameters, c, and a positive
distance between training and testing contexts, in order for an instance
model to predict a pattern of varied training from stimuli 400 and 800
outperforming constant training from position 600 at a test position of
600. For the top left panel, in which the generalization model assumes a
single c value (-.008) for both varied and constant conditions, and
identical contexts across training and testing, the equation which
generates the varied condition is - Amount of Generalization =
\(e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}\), whereas the constant
group generalization is generated from \(2\cdot e^{(c\cdot|x-600|)}\).
For the top right panel, the c constants in the original equations are
different for the 2 conditions, with \(c=-.002\) for the varied
condition, and \(c=-.008\) for the constant condition. The bottom two
panels are generated from identical equations to those immediately
above, except for the addition of extra distance (100 units) to reflect
the assumption of some change in context between training and testing
conditions. Thus, the generalization model for the varied condition in
the bottom-right panel is of the form - Amount of Generalization =
\(e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}\) .}

\end{figure}%

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# print(getwd())}
\CommentTok{\# here::set\_here(path=\textquotesingle{}..\textquotesingle{})}
\CommentTok{\# print(getwd())}
\FunctionTok{source}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"Functions"}\NormalTok{, }\StringTok{"packages.R"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{test }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"data/e1\_08{-}21{-}23.rds"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} \FunctionTok{filter}\NormalTok{(expMode2 }\SpecialCharTok{==} \StringTok{"Test"}\NormalTok{)  }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(id,condit,bandInt,vb,vx,dist,sdist,bandType,tOrder)}
\end{Highlighting}
\end{Shaded}

\paragraph{Posterior Predictive
Distributions}\label{posterior-predictive-distributions}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dist\_pred }\OtherTok{\textless{}{-}} 
  \FunctionTok{posterior\_predict}\NormalTok{(e1\_distBMM, }\AttributeTok{ndraws =} \DecValTok{500}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{array\_branch}\NormalTok{(}\AttributeTok{margin=}\DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
   \FunctionTok{map\_dfr}\NormalTok{( }
    \ControlFlowTok{function}\NormalTok{(yrep\_iter) \{}
\NormalTok{      test  }\SpecialCharTok{|\textgreater{}}
        \FunctionTok{mutate}\NormalTok{(}\AttributeTok{dist\_pred =}\NormalTok{ yrep\_iter)}
\NormalTok{    \},}
    \AttributeTok{.id =} \StringTok{\textquotesingle{}iter\textquotesingle{}}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{iter =} \FunctionTok{as.numeric}\NormalTok{(iter))}

\NormalTok{dist\_pred  }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{filter}\NormalTok{(iter }\SpecialCharTok{\textless{}} \DecValTok{100}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(dist\_pred, }\AttributeTok{group =}\NormalTok{ iter)) }\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{03}\NormalTok{, }\AttributeTok{stat =} \StringTok{\textquotesingle{}density\textquotesingle{}}\NormalTok{, }\AttributeTok{color =} \StringTok{\textquotesingle{}blue\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_density}\NormalTok{(}\AttributeTok{data =}\NormalTok{ test,}
               \FunctionTok{aes}\NormalTok{(dist,}\AttributeTok{col=}\NormalTok{vb),}
               \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{,}
               \AttributeTok{size =} \FloatTok{0.7}\NormalTok{) }\SpecialCharTok{+} \CommentTok{\# 1}
  \FunctionTok{facet\_grid}\NormalTok{(condit }\SpecialCharTok{\textasciitilde{}}\NormalTok{ vb) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{\textquotesingle{}Deviation\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

\centering{

\includegraphics{igas_e1_files/figure-pdf/fig-post-pred-dist-1.pdf}

}

\caption{\label{fig-post-pred-dist}Posterior Predictive distributions
for Absolute Deviance. Posterior Draws in Blue, colored lines are
empirical data.}

\end{figure}%

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{vx\_pred }\OtherTok{\textless{}{-}} 
  \FunctionTok{posterior\_predict}\NormalTok{(e1\_vxBMM, }\AttributeTok{ndraws =} \DecValTok{500}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{array\_branch}\NormalTok{(}\AttributeTok{margin=}\DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
   \FunctionTok{map\_dfr}\NormalTok{( }
    \ControlFlowTok{function}\NormalTok{(yrep\_iter) \{}
\NormalTok{      test  }\SpecialCharTok{|\textgreater{}}
        \FunctionTok{mutate}\NormalTok{(}\AttributeTok{vx\_pred =}\NormalTok{ yrep\_iter)}
\NormalTok{    \},}
    \AttributeTok{.id =} \StringTok{\textquotesingle{}iter\textquotesingle{}}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{iter =} \FunctionTok{as.numeric}\NormalTok{(iter))}

\NormalTok{vx\_pred  }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{filter}\NormalTok{(iter }\SpecialCharTok{\textless{}} \DecValTok{100}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(vx\_pred, }\AttributeTok{group =}\NormalTok{ iter)) }\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{03}\NormalTok{, }\AttributeTok{stat =} \StringTok{\textquotesingle{}density\textquotesingle{}}\NormalTok{, }\AttributeTok{color =} \StringTok{\textquotesingle{}blue\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_density}\NormalTok{(}\AttributeTok{data =}\NormalTok{ test,}
               \FunctionTok{aes}\NormalTok{(vx,}\AttributeTok{col=}\NormalTok{vb),}
               \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{,}
               \AttributeTok{size =} \FloatTok{0.7}\NormalTok{) }\SpecialCharTok{+} \CommentTok{\# 1}
  \FunctionTok{facet\_grid}\NormalTok{(condit }\SpecialCharTok{\textasciitilde{}}\NormalTok{ vb) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{\textquotesingle{}Vx\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

\centering{

\includegraphics{igas_e1_files/figure-pdf/fig-post-pred-vx-1.pdf}

}

\caption{\label{fig-post-pred-vx}Posterior Predictive distributions for
Vx. Posterior Draws in Blue, colored lines are empirical data.}

\end{figure}%

\paragraph{Empirical vs.~Predicted}\label{empirical-vs.-predicted}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{\{}
\NormalTok{vx\_pred  }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{filter}\NormalTok{(iter }\SpecialCharTok{\textless{}} \DecValTok{100}\NormalTok{)  }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(id,condit,vb,iter) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{vx\_pred=}\FunctionTok{mean}\NormalTok{(vx\_pred)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{vb,}\AttributeTok{y=}\NormalTok{vx\_pred,}\AttributeTok{fill=}\NormalTok{condit)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_flat\_violin}\NormalTok{( }\AttributeTok{position =} \FunctionTok{position\_nudge}\NormalTok{(}\AttributeTok{x =} \FloatTok{0.1}\NormalTok{, }\AttributeTok{y =} \DecValTok{0}\NormalTok{),}
                   \AttributeTok{adjust =} \FloatTok{1.5}\NormalTok{,}
                   \AttributeTok{trim =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{5}\NormalTok{, }\AttributeTok{colour =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{+}
